The Hot Hand Fallacy in Call of Duty Search and Destroy

### 2022-08-25 paper/paper.Rmd
anonymize

---
title: "The Hot Hand Fallacy in Call of Duty Search and Destroy"
authors:
  - name: Person One
    email: personone@domain.com
  - name: Person Two
    email: persontwo@domain.com
abstract: |
  Our research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD). First, we find evidence supporting the hypothesis that round win probability can be modeled as a constant across rounds in the series, although not at the naive 50%. Second, we examine the proportion of round wins immediately following a win streak. Given streak length, series length, and series winner, we find no evidence that post-streak win proportion is significantly different than expected, suggesting that the perception of momentum at the team level is deceiving. Wald-Wolfowitz run tests also fail to provide evidence for the hot hand phenomenon.
bibliography: references.bib
keywords:
  - esports
  - Call of Duty
  - hot hand
  - runs test
output:
  rticles::arxiv_article:
    includes:
      in_header: preamble.tex
---

>>>>

---
title: "The Hot Hand Fallacy in Call of Duty Search and Destroy"
authors:
  - name: Person One
    email: personone@domain.com
  - name: Person two
    email: persontwo@domain.com
abstract: |
  Our research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD). First, we find evidence supporting the hypothesis that round win probability can be modeled as a constant across rounds in the series, although not at the naive 50%. Second, we examine the proportion of round wins immediately following a win streak. Given streak length, series length, and series winner, we find no evidence that post-streak win proportion is significantly different than expected, suggesting that the perception of momentum at the team level is deceiving. Wald-Wolfowitz run tests also fail to provide evidence for the hot hand phenomenon.
bibliography: references.bib
keywords:
  - esports
  - Call of Duty
  - hot hand
  - runs test
output:
  rticles::arxiv_article:
    includes:
      in_header: preamble.tex
---
